### 2010-12-06 report/report.tex
in progress

\section{Introduction}
% Motivate and abstractly describe the problem you are addressing and
% how you are addressing it. What is the problem? Why is it important?
% What is your basic approach? A short discussion of how it fits into % related work in the area is also desirable. Summarize the basic results
% and conclusions that you will present.

>>>>

\section{Introduction}

% Motivate and abstractly describe the problem you are addressing and
% how you are addressing it. What is the problem? Why is it important?
% What is your basic approach? A short discussion of how it fits into
% % related work in the area is also desirable. Summarize the basic
% results and conclusions that you will present.

Applications of walking robots often call for the ability to walk as
quickly, efficiently, or with as little power as possible.
Oftentimes, these optimizations are done manually by an expert who
designs a gait to be, for example, as fast as possible \cite{someone}.  Some groups (Kohl and Stone) have

Previous
Walking robots often have

Many previous walking robots have had walking motions -- or gaits --
designed and tweaked by hand \cite{someone,else}, or in some cases, beginning with a
